Appendix

### 2017-10-20 code/appendix.Rmd
WIP

>>>>

# Stochastic oscillator

```{r}
p <- list(r = .5, K = 2, Q = 5, H = .38, sigma = .04, a = 0.245, N = 1e4)

f <- function(x) x * p$r * (1 - x / p$K)
g <- function(x) p$a * x ^ p$Q / (x^p$Q + p$H^p$Q)

x <- seq(0,2, length.out = 100)
data.frame(x, f = f(x), g = g(x)) %>%
  ggplot(aes(x)) + geom_line(aes(y = f-g)) + 
  geom_hline(aes(yintercept=0), lty=2) +
  coord_cartesian(xlim = c(0,1.5), ylim=c(-.015,.1))

```{r}
system.time({
may  <- nimble::nimbleCode({

  x[1] <- x0
  for(t in 1:(N-1)){
    mu[t] <- x[t] + x[t] * r * (1 - x[t] / K)  - a * x[t] ^ Q / (x[t] ^ Q + H ^ Q)
    y[t+1] ~ dnorm(mu[t], sd = sigma)
    x[t+1] <- max(y[t+1],0)
  }

model <- nimbleModel(may,constants = p, inits = list(x0 = 1.2))
cmodel <- compileNimble(model)
set.seed(123)

simulate(cmodel)
df <- tibble(t = seq_along(cmodel$x), x = cmodel$x)
})

df  %>% ggplot(aes(t,x)) + geom_line()
```

# Tipping points

Needs a model with non-zero alternate state!

tip  <- nimble::nimbleCode({

  x[1] <- x0
  for(t in 1:(N-1)){
    mu[t] <- x[t] + x[t] * r * (1 - x[t] / K) * (x[t] - A) / K - h[t]
    y[t+1] ~ dnorm(mu[t], sd = sigma)
    x[t+1] <- max(y[t+1],0)
  }

p <- list(r = .2, K = 1, A = 0.2, sigma = .01, N = 500, h = seq(0,.03,length=500))

model <- nimbleModel(tip,constants = p, inits = list(x0 = 1))
cmodel <- compileNimble(model)
set.seed(123)

simulate(cmodel)
df <- tibble(t = seq_along(cmodel$x), x = cmodel$x)

```{r}
df %>% ggplot(aes(t,x)) + geom_line()
```
